Estimating duration in the presence of misclassification

### 2024-02-05 transmission.tex

\todo[inline]{Rewrite the intro: eg see Dani's Overleaf comments}

@@

@@

During such an exponential growth phase, all components of the $\vec{e}$, $\vec{i}$ and $\vec{p}$ compartments grow at the same growth rate, $\psi$.
This follows directly from the ODEs if $\vec{s}$ is constant. 
The growth rate $\psi$ is easily identifiable from the data, and therefore a parameterisation in terms of $\phi$ should be more computationally efficient.
If this is the initial exponential phase, when $\vec{s} \approx 1$, then the basic reproduction number for a SEIR model is linked to this growth rate by~\autocite{birrellBayesian,wearingAppropriate}:
\begin{align}
    \R = \frac{\psi \left( \frac{\psi}{2\sigma} + 1 \right)^2}{\gamma \left(1 - \frac{1}{\left(\frac{\psi}{2 \gamma} + 1 \right)^2} \right)} \label{SEIR:eq:rtoR}.
\end{align}

>>>>

\todo[inline]{Intro probably needs rewriting, with novelty claims and a bit more context. Revisit once intro chapters written.}

@@

The deterministic relationship between incidence proportion and prevalence means that either can be inferred, with the other then calculated.
Denote the quantity to be inferred at time $t$ is strata $i$ as $\pi_{it}$.
Note that for any $i$ and $t$, the number of positives will be small, often fewer than 5; therefore some form of borrowing between time and strata is required.
The statistical model used for inference, including the borrowing of information, should have the following properties.
\begin{itemize}
    \item The smoothing model should penalise towards exponential growth.
        Penalising towards exponential growth is a natural formulation because mechanistic models predict exponential growth over short periods of time.
        Furthermore, such penalisation has previously been shown to improve estimates of prevalence by balancing over and under-fitting~\autocite{ealesAppropriately}.
\end{itemize}

@@

During such an exponential growth phase, all components of the $\vec{e}$, $\vec{i}$ and $\vec{p}$ compartments grow at the same growth rate, $\psi$.
This follows directly from the ODEs if $\vec{s}$ is constant. 
The growth rate $\psi$ is easily identifiable from the data, and therefore a parameterisation in terms of $\psi$ should be more computationally efficient.
If this is the initial exponential phase, when $\vec{s} \approx 1$, then the basic reproduction number for a SEIR model is linked to this growth rate by~\autocite{birrellBayesian,wearingAppropriate}:
\begin{align}
    \R = \frac{\psi \left( \frac{\psi}{2\sigma} + 1 \right)^2}{\gamma \left(1 - \frac{1}{\left(\frac{\psi}{2 \gamma} + 1 \right)^2} \right)} \label{SEIR:eq:rtoR}.
\end{align}
